Deep Neural Networks for Bilingual Lexicon Extraction

### 2014-06-07 paper/main.tex
Add note in future work about using actual distance measure values

\subparagraph{Near misses.} In these cases the algorithm mapped into a precise
neighborhood of related words, but picked the wrong element from the set. For
example, the output word \textit{chocolate} is strongly related to the expected
word \textit{vainilla}. % TODO long paper: future work might examine
% the actual distance values and "give up" if the top few words are all very
% close

@@

>>>>

\subparagraph{Near misses.} In these cases the algorithm mapped into a precise
neighborhood of related words, but picked the wrong element from the set. For
example, the output word \textit{chocolate} is strongly related to the expected
word \textit{vainilla}. We describe a possible solution to this type of error in
\Cref{sec:conclusion}.

@@

As mentioned in \Cref{subsec:error-analysis}, a substantial amount of
translation errors encountered during testing were due to ``near misses'': an
incorrect selection of a target-language word from a correctly-chosen precise
semantic neighborhood. Future work might examine the actual distance values
between the algorithm's target-language vector output and the target-language
word vectors which we compare to, and make more intelligent translation choices
(perhaps refusing to provide exactly one output value) when the translation
seems too semantically ambiguous. % TODO unclear?
